An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-21 poly-embed-journal/poly-embed-journal.tex
Some comments on book chapter section and confirming statements we want

\subsection{Embedding}
\jessiet{Also, do we want to frame calibrated links as ``loose embeddings''? Lol}
\raft{Ew}

@@

\begin{claim}
	For all $x\in\reals^\Y_+$, there exists $v\in\V^*$ such that $H_v$ supports $G$ at $(x,g(x))$.
\end{claim}
\begin{proof}
We can write any face $F_v = H_v \cap G = \{x \in \reals_+^{d-1} \mid \inprod{x}{v} = g(x)\}$.
If there was no $v \in \V^*$ such that $x \in F_v$, then $g(x) = \min_{H_v \in \H_\Y} \inprod{v}{x}$.
As these halfspaces are vertical, we have $g(x) = -\infty$, which does not support $G$ at $(x, g(x))$ since $x \in \reals_+^\Y$, yielding a contradiction.
\jessie{Don't like this. Slash not true.  There's something implicit about all the normals being in $\R^d_-$ and $x \in \reals^d_+$.  Haven't proven the first claim}
%We claim $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.
%If there was a $v \in \V$ such that $\pi(F_v) \not \subseteq \reals_+^\Y$, this would imply there is some $x \not \in \reals_+^\Y$ such that $\inprod{x}{v} = c < \infty = g(x)$, contradicting $F_v$ supporting $g$ at $x$.
%Thus, $\cup_{v \in \V} \pi(F_v) \subseteq \reals_+^\Y$.
%Now for the other direction of subset inclusion, observe that for all $x \in \reals^\Y_+$, we have $g(x) = f(x) = \min_{v \in \V}\inprod{v}{x}$, so there is a $v \in \V$ supporting $g$ at $x$, and therefore $x \in \pi(F_v)$ for some $v \in \V$, and is therefore in the union of projections.
%As we have shown both directions of set inclusion, we must have $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.	
\end{proof}

@@

\begin{claim} 
For all $v\in\reals^\Y_+$, if $H_v$ supports $G$,  $\dim(\pi(F_v)) = \dim(F_v)-1$.
\end{claim}
\begin{proof}
	\jessie{TODO}
	$F_v = \H_v \cap G \neq \emptyset$ by assumption.
	$\dim(F_v) = \dim(\affhull(F_v))$
	$\dim(\pi(F_v)) = \dim(F_v) - 1$.
\end{proof}

@@

\begin{claim}If a $H_v \in \H$ does support $G$, then $F_{v} = H_{v} \cap G$ is a face of $G$, and thus a subset of a facet.
\end{claim}
\begin{claim}
	For any $v \in \V$, the face $F_{v}$ must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
\end{claim}
\begin{claim}
	Thus, $\pi(F_{\hat v}) \subseteq \pi(F_v)$. \raf{This will show (3) once we translate back}
\end{claim}
\begin{claim}
	$\R'$ is a rep set for $L$ if and only if $\V \subseteq L(\R')$.
\end{claim}
\begin{corollary}
	$\R^*$ is a min rep set for $L$ if and only if $\V^* = L(\R^*)$. \raf{(1)}
\end{corollary}

>>>>

\subsection{Embedding}

@@

\begin{claim}
	For all $x\in\reals^\Y_+$, there exists $v\in\V^*$ such that $H_v$ supports $G$ at $(x,g(x))$.
\end{claim}
\begin{proof}
We can write any face $F_v = H_v \cap G = \{x \in \reals_+^{d-1} \mid \inprod{x}{v} = g(x)\}$.
Since $H_v^+$ must be a valid inequality to define a face, we know that $G \subseteq H_v^+$.
If there was no $v \in \V^*$ such that $x \in F_v$, 
Since $\H_\V = \H_\Y \cup \H_{\V^*}$, if there was no $v \in \V^*$ such that $x \in F_v$, it must be the case that $\min_{H_v \in \H_\Y} \inprod{v}{x} = \min_{y \in \Y} x_y = 0 = g(x)$, and we must have $x \not \in \reals_{++}^\Y$.

\jessie{If $G$ is not locally constant}
Since $g$ is continuous (as it is convex), and not constant \jessie{??}, there must be some $x' \in B(x,\epsilon) \cap \reals_+^\Y$ such that $g(x') > 0$ and therefore no $y \in \Y$ would define a face $F_{v^*}$ supporting $G$ at $x'$.
That $v^*$ must then be in $\V^*$, and we claim $\inprod{v^*}{x} = 0$, which would imply $F_{v^*}$ also supports $G$ at $x$.
If $\inprod{v^*}{x} > 0 = g(x)$ (recall $g$ nonnegative on $\reals_+^\Y$) then we contradict continuity of $g$ on $\reals_+^\Y$. \jessie{Not the level of rigor that we want.  Also using lots of polyhedral structure here.}
%First, $\inprod{v^*}{x} \geq 0$ by definition of $g$ nonnegative on $\reals_+^\Y$, and $\leq 0$

\jessie{Claim: $x$ must be on boundary of $\reals_+^\Y$ and therefore $g(x) = 0$, and we have a matchy matchy with a $v^* \in \V^*$.}

\jessie{If $x \in \reals_{++}^\Y$, then}

%As these halfspaces are vertical, we have $g(x) = -\infty$, which does not support $G$ at $(x, g(x))$ since $x \in \reals_+^\Y$, yielding a contradiction.
%\jessie{Don't like this. Slash not true.  There's something implicit about all the normals being in $\R^d_-$ and $x \in \reals^d_+$.  Haven't proven the first claim}
%We claim $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.
%If there was a $v \in \V$ such that $\pi(F_v) \not \subseteq \reals_+^\Y$, this would imply there is some $x \not \in \reals_+^\Y$ such that $\inprod{x}{v} = c < \infty = g(x)$, contradicting $F_v$ supporting $g$ at $x$.
%Thus, $\cup_{v \in \V} \pi(F_v) \subseteq \reals_+^\Y$.
%Now for the other direction of subset inclusion, observe that for all $x \in \reals^\Y_+$, we have $g(x) = f(x) = \min_{v \in \V}\inprod{v}{x}$, so there is a $v \in \V$ supporting $g$ at $x$, and therefore $x \in \pi(F_v)$ for some $v \in \V$, and is therefore in the union of projections.
%As we have shown both directions of set inclusion, we must have $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.	
\end{proof}

@@

\begin{claim} 
For all $v\in\reals^\Y_+$, if $H_v$ supports $G$,  $\dim(\pi(F_v)) = \dim(F_v)-1$.
\end{claim}
\begin{proof}
	\jessie{TODO}
	Facts we can potentially use:
	$F_v = \H_v \cap G \neq \emptyset$ by assumption.
	$\dim(F_v) = \dim(\affhull(F_v))$
	$\dim(\pi(F_v)) = \dim(F_v) - 1$.
\end{proof}

@@

\begin{claim}If a $H_v \in \H$ does support $G$, then $F_{v} = H_{v} \cap G$ is a face of $G$, and thus a subset of a facet.
\end{claim}
\begin{proof}
	Since $H_v$ supports $G$, we know that $G \subseteq H_v^+$ (WLOG) and $F_v$ is not empty.
	Since $H^+_v$ is valid, we have $F_v = F_{([v;-1],0)}$ is a face by definition.

	%subset of facet
	Moreover, the faces of $G$ are all convex polyhedra.
	Any face of $G$ is must then be a lower-dimensional face of a facet, and therefore a subset.
\end{proof}

\begin{claim}
	For any $v \in \V$, the face $F_{v}$ must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
	\jessie{I don't think this is true as stated.  I think this is true for non-facets, but this implies that any $H_y \in \H_\Y$ doesn't support $G$}
\end{claim}
\begin{proof}
%	Suppose $F_v \subseteq F_{v^*}$.
%	If $v' \not \in \V^*$, then $v' = [e_y; 0]$ for some $y \in \Y$.
%	By construction of $G$, the polyhedron shoots off to $-\infty$, so the only subfaces of $F_{v'}$ are also adjacent 
%	\jessie{Very informal...} 
\end{proof}

\begin{corollary}
	For $v,v^*$ such that $F_v \subseteq F_{v^*}$ and $v^*\in \V^*$, $\pi(F_{v}) \subseteq \pi(F_{v^*})$. \raf{This will show (3) once we translate back}
\end{corollary}
\begin{claim}
	$\R'$ is a representative set for $L$ if and only if $\V \subseteq L(\R')$.
	\jessie{Is this true?  You could have hinge with a really bad loss vector that is never uniquely optimal (ex: $u = 2$) and $(3,0) \in L(\R)$ but not in $L(\{-1,1\})$.}
\end{claim}

\begin{corollary}
	$\R^*$ is a min rep set for $L$ if and only if $\V^* = L(\R^*)$. \raf{(2)}
\end{corollary}
